Maximising the guaranteed feasible set for stochastic MPC with chance constraints

### 2016-11-08 draft.tex
version submitted 8 Nov

\title{Maximising the guaranteed feasible set for uncertain MPC schemes with chance constraints}%\thanksref{footnoteinfo}} 
% Title, preferably not more than 10 words.

@@

\begin{keyword}                           % Five to ten keywords,  
Robust control; chance constraints; stochastic MPC; positively invariant sets.
\end{keyword}                             % keyword list or with the 
                                          % help of the Automatica 
                                          % keyword wizard

@@

In order to determine an algorithm to compute $X^\infty$ we rewrite the conditions in~\eqref{eq:alternative:MRPI:set} by introducing the set of all possible successor states~$\D_k(X)$ of states in $X$ after $k$ time steps:
%
\begin{align*}
	\D_k(X) &= (A+BK)^{k}X\oplus\W\oplus\dots\oplus(A+BK)^{k-1}\W\\
	&= (A+BK)^k X\oplus \bigoplus_{i=0}^{k-1}(A+BK)^i\W
\end{align*}
%
Defining $\R = (C+DK)^{-1}(\Y\ominus\V^\prime)$ we can abbreviate the conditions defining $X^\infty$ in~\eqref{eq:alternative:MRPI:set} to
%
\begin{equation}\label{eq:containment:condition:alternative:MRPI}
\D_k(X^\infty)\subseteq\X\cap\R
\end{equation}
%
for all $k\geq0$.
%
Using these conditions we can express $X^\infty$ directly as
%
\begin{gather}
X^\infty = %\bigcap_{k\geq0}(A+BK)^{-k}\Bigl((\X\cap\R)\ominus\bigoplus_{i=0}^{k-1}(A+BK)^i\W\Bigr) \\
\bigcap_{k\geq0} \E_k, \\
\E_k = (A+BK)^{-k}\biggl[(\X\cap\R)\ominus\bigoplus_{i=0}^{k-1}(A+BK)^i\W\biggr] . \label{eq:Ek:subtract}
\end{gather}
% \begin{equation}\label{eq:direct:formulation:MRPI:with:intersection}
% 	X^\infty = \bigcap_{k\geq0}\underbrace{(A+BK)^{-k}\left((\X\cap\R)\ominus\bigoplus_{i=0}^{k-1}(A+BK)^i\W\right)}_{\E_k}.
% \end{equation}
%
Due to its definition~$\E_k$ satisfies $\D_k(\E_k)\subseteq\X\cap\R$ for each $k\geq0$, furthermore it can be shown that $\E_k$ expands exponentially and therefore $X^\infty$ is finitely determined  (see Theorem~\ref{thm2} below).
%
In order to compute $X^\infty$ we define the sequence $X_0,X_1,\ldots$ via the iteration:
%
\begin{equation}\label{eq:MRPI:sequence}
\begin{aligned}
  & X_0 = \X \\
  & \begin{aligned}
      & Z_k = X_k\cap\R\\
      & X_{k+1} = Z_k\cap(A+BK)^{-1}(Z_k\ominus\W)
    \end{aligned} 
  \ \Biggr\} \ \ k = 1,2,\ldots
\end{aligned}
\end{equation}
%
%with $X_0= \X$.
Clearly $X_k = \bigcap_{l=0,\ldots,k}\E_l$ and, analogously to the conventional MRPI calculation~\citep{Kolmanovsky:1998}, the iteration therefore gives $X_k = X^\infty$ if $X_k\subseteq X_{k+1}$.

\vspace{0.5\baselineskip}
\begin{thm}\label{thm2}
Let $\Gamma$ be a matrix such that $\Gamma x\leq\bfa{1}$ and $-\Gamma x\leq\bfa{1}$ for all $x\in\X$ and let $\bigl((A+BK),\Gamma\bigr)$ be observable, then the iteration~\eqref{eq:MRPI:sequence} %terminates after a finite number, $N$, of iterations, such that 
yields $X_{k+1}=X_k$ for all $k\geq N$ and hence $X_k=X^\infty$ for some finite integer $N$.
\end{thm}
%
\bpf
%
The observability of the pair $\bigl((A+BK),\Gamma\bigr)$ implies that $X_{d-1}$ is compact, since 
\begin{align*}
X_{d-1} 
&\subseteq\bigcap_{k\leq d-1}(A+BK)^{-k}\X\\
&\subseteq \Bigl\{x:\pm\Gamma x\leq\bfa{1}\wedge\dots\wedge\pm\Gamma(A+BK)^{d-1} x\leq\bfa{1} \Bigr\}\\
& = \bigl\{x:\pm\Gamma \Obs x\leq \bfa{1}\bigr\}
\end{align*}
where $\Obs$ is the (full rank) observability matrix.

Let~$P$ be such that 
\[
(A+BK)^TP(A+BK) \leq \rho^2P
\]
holds, where $\rho$ denotes the spectral radius of $A+BK$.
%
To see that $\E_k$ grows exponentially let $\W\subseteq\B_P(r)$ then
%
\begin{multline*}
  \bigoplus_{i=0}^{k-1}(A+BK)^i\W \subseteq \bigoplus_{i=0}^{k-1}(A+BK)^i\B_P(r)\\
  \subseteq\bigoplus_{i=0}^{k-1}\B_P(\rho^i r) = \B_P\biggl(\sum_{i=0}^{k-1}\rho^i r\biggr)\subseteq\B_P\Bigl(\frac{r}{1-\rho}\Bigr) .
\end{multline*}
%
It follows that the subtrahend in square brackets on the RHS of (\ref{eq:Ek:subtract}) is bounded for all $k$ by $\B_P\bigl(r / (1-\rho)\bigr)$.
%It follows that the RHS of (\ref{eq:Ek:subtract}) consists of an expanding minuend and a bounded subtrahend.
%
Therefore 
%$\E_k$ expands exponentially. Hence 
the iteration (\ref{eq:MRPI:sequence}) must either yield $X_N = \emptyset$ for finite $N$
(in which case $X^\infty=\emptyset$) or,
since $X_{d-1}$ is bounded and $\E_k$ expands exponentially, there must exist a finite $N$ such that $X_{N}\cap\E_{N+1}=X_N$ and hence $X_N=X^\infty$.
%
\epf

@@

In particular, the one-step controllable set $C_1(\T)$ for a polytopic
target set~$\T$
% \[
% \T = \Bigl\{x\in\RR^d : J_i x\leq1,\ i\leq M_\T\Bigr\}
% \]
% is given by the projection of 
%
%In particular, the one-step controllable set $C_1(\T)$ for the polytopic target set~$\T$
% \[
% \T = \Bigl\{x\in\RR^d : J_i x\leq1,\ i\leq M_\T\Bigr\}
% \]
is given by the projection on to the $x$-subspace of the polytopic set $L_1(\T)\subset \RR^{d+q_{\U}}$, 
%$L_1(\T)\subset \RR^d\times \RR^{q_{\U}}$, 
defined by
%
\begin{multline*}
L_1(\T) = \Bigl\{(x,u)\in (\X,\U): \\
\begin{aligned}
& Cx+Du + v\in\Y \\
& Ax+Bu+w\in\T
\end{aligned}\\
\forall v\in\V^\prime,\, \forall w\in\W\Bigr\} .
%\end{aligned}
\end{multline*}
% \begin{equation}
% 	L_1(\T) = \left\{(x,u):\begin{aligned}
% 	x\in\X, u\in\U, Cx+Du + v\in\Y\;\forall v\in\V^\prime,\\
% 	Ax+Bu+w\in\T\;\forall w\in\W
% 	\end{aligned}\right\}
% \end{equation}
%
%onto the $x$-subspace.
%
Thus
\[
C_1(\T) = \{ x : \exists u \ \text{such that} \ (x,u)\in L_1(\T)\}.
\]
As all involved sets are polytopic, $L_1(\T)$ is polytopic and its exact projection can be determined computationally.

@@

In order to compare the proposed method with existing results we compute a sample-based set as described in~\cite{Zhang2015}, that is we compute the smallest set $\V^\prime$ containing enough samples to guarantee constraint satisfaction with a confidence of $1-\beta$.
%
To obtain a comparable result we use again constrain $\V^\prime $ to be a scaled version of $\V$, so that $\V^\prime = \{v : \Gamma_i v \leq \gamma_i, \, i =1,\ldots,4\}$, where $\V = \{v : \Gamma_i v \leq 1, \, i =1, \ldots ,4\}$.
%
The optimisation~\citep[eq.~(10)]{Zhang2015} is then given as
%
\begin{subequations}\label{eq:comparison:set}
\begin{equation}\min_{\gamma_1,\dots,\gamma_4} \  \ \sum_{i=1}^4\gamma_i
\end{equation}
subject to 
\begin{equation}
\Gamma_i \hat{v}^{(j)}\leq \gamma_i ,\ i\in\{1,\ldots,4\}, \ j = 1,\ldots,N
\end{equation}
\end{subequations}
% \begin{equation}\label{eq:comparison:set}\begin{split}
% 	\min_{\gamma_1,\dots,\gamma_4}&\quad\sum_{i=1}^4\gamma_i\\
% 	\text{s.t.}&\quad \Gamma_i \bfa{v}^{(j)}\leq \gamma_i ,i\in\{1,\dots,4\}
% \end{split}\end{equation}
%
%$\hat{v}^{(j)}$, $j=1,\ldots,N$ 
where $\hat{v}^{(1)},\ldots,\hat{v}^{(N)}$
are the samples used to satisfy the probabilistic requirements with the  given confidence of $\beta=0.001$. The number of samples that are needed to satisfy this requirement is given by the cumulative binomial distribution, but can be overestimated to be $N \geq \frac{2}{\beta}(2-\log(p))$, so for this example $N = 4714$.
%

The resulting sets $\V^\prime$ and $X^\infty$ are shown in Figures~\ref{figure:V:prime:and:comparison} and~\ref{fig:MRPI:optimised}. 
%
The set $\V^\prime$ computed using (\ref{eq:comparison:set}a,b) is clearly suboptimal (Fig.~\ref{figure:V:prime:and:comparison}), and in fact it contains $99.91$\% of the total volume of $\V$. 
This suboptimality is a result of the requirement for a high level of confidence ($1-\beta = 0.999$), and is reflected in a reduction in volume of the associated positively invariant set (Fig.~\ref{fig:MRPI:optimised}).

%
\begin{figure}
\includegraphics[width=0.99\linewidth]{Vprime.pdf}
\caption{The set~$\V^\prime$ resulting from the
  optimisation \mbox{(\ref{seq:optimisation:MRPI:precise}a-d)}
with
  $\PP\{v\in\V^\prime\}=0.3$
in \textcolor[rgb]{0.9255,0.6902,0.2078}{yellow}. In \textcolor{red}{red}, the set $\V^\prime$
  computed using~(\ref{eq:comparison:set}a-b) for a confidence level of $1-\beta=0.999$. The 
  samples $\{\hat{v}^{(j)},\ldots,\hat{v}^{(N)}\}$ are shown in \textcolor{blue}{blue}.}
\label{figure:V:prime:and:comparison}
\vspace{2mm}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.99\linewidth]{MRPIsetOptimised.pdf}
% \caption{The guaranteed positively invariant set of the system~\eqref{eq:example:system:MRPI} in solid red, in dashed blue the robust positively invariant set for the disturbance set computed with the methods discussed in~\cite{Zhang2015}.}
\caption{The guaranteed positively invariant set $X^\infty$ computed using
\mbox{(\ref{seq:optimisation:MRPI:precise}a-d)}
%(\ref{seq:optimisation:MRPI:abstract}a-c) 
%of the system~\eqref{eq:example:system:MRPI} 
in \textcolor{red}{red}, and in \textcolor{blue}{blue} the robust positively invariant set for the disturbance set $\V^\prime$ computed using~(\ref{eq:comparison:set}a-b)
with a confidence level of $1-\beta = 0.999$.}
\label{fig:MRPI:optimised}
\vspace{2mm}\end{figure}

% For the same setup~\eqref{eq:example:system:MRPI} we approximate the guaranteed 3-step controllable set $\C_3(\T)$, where $\T=X^\infty$.
% %
% Again the result illustrated in Figure~\ref{fig:n:step:controllable:set} can be reproduced using different initial values although the Hessian at the maximiser has a non-trivial nullspace.
%
For the same system and constraints (\ref{eq:example:system:MRPI})-(\ref{eq:example:pconstriaint}) we approximate the guaranteed 3-step controllable set $\C_3(\T)$, with $\T=X^\infty$,
%
by solving (\ref{seq:optimisation:n:step:precise}a-d) for $C_1(X^\infty)$, $C_2(X^\infty)$, $C_3(X^\infty)$, where $X^\infty$ is the guaranteed positively invariant set computed via (\ref{seq:optimisation:MRPI:precise}a-d).
%
Again the results illustrated in Figure~\ref{fig:n:step:controllable:set} are reproduced using different initial values even though the Hessian at the maximiser has a non-trivial nullspace. The figure also shows the controllable sets that are obtained, for the same target set (i.e.~$\T=X^\infty$), with a fixed set $\V^\prime$ which was computed using the sample based approach of~\citet{Zhang2015} by solving~(\ref{eq:comparison:set}a-b). Clearly the high level of suboptimality in this choice of $\V^\prime$, 
which is a consequence of 
%that results from 
the requirement for a high level of confidence of satisfaction of the chance constraint, translates to suboptimality in the computed sets $C_n(X^\infty)$.
%
% For the same system and constraints (\ref{eq:example:system:MRPI})-(\ref{eq:example:pconstriaint}) we approximate the guaranteed 3-step controllable set $\C_3(\T)$, where $\T=\{x:\norm{x}_\infty\leq 2\}$
% %
% by solving (\ref{seq:optimisation:n:step:set:abstract}a-c) for $C_1(\T)$, $C_2(\T)$, $C_3(\T)$.
% %
% Again the result illustrated in Figure~\ref{fig:n:step:controllable:set} is reproduced using different initial values although the Hessian at the maximiser has a non-trivial nullspace.
% %

\begin{figure}[ht]
\includegraphics[width=.99\linewidth]{NStepSetOptimised.pdf}
% \caption{Approximation of the guaranteed 3-step controllable set for a guaranteed positive invariant set $X^\infty$ (in blue). The additional sets are remaining $C_1(X^\infty),C_2(X^\infty)$ and $C_3(X^\infty)$ dashed for the comparison set obtained with~\eqref{eq:comparison:set} and solid for the optimised~$\V^\prime$ obtained with the proposed method.}
\caption{Approximation of the guaranteed 3-step controllable set for a $\T=X^\infty$ (in \textcolor{blue}{blue}). Sets $C_1(\T)$, $C_2(\T)$ and $C_3(\T)$ computed by optimising $\V^\prime$ using  (\ref{seq:optimisation:n:step:set:abstract}a-c) are shown in solid lines. For comparison, the controllable sets obtained for a fixed $\V^\prime$ computed using~(\ref{eq:comparison:set}a,b) with 
confidence $1-\beta= 0.999$ are shown in dashed lines.}
\label{fig:n:step:controllable:set}
\vspace{4mm}\end{figure}

>>>>

\title{Maximising the guaranteed feasible set for stochastic MPC with chance constraints}%\thanksref{footnoteinfo}} 
% Title, preferably not more than 10 words.

@@

\begin{keyword}                           % Five to ten keywords,  
Robust control; chance constraints;  invariant sets; stochastic MPC.
\end{keyword}                             % keyword list or with the 
                                          % help of the Automatica 
                                          % keyword wizard

@@

In order to determine an algorithm to compute $X^\infty$ we rewrite the conditions in~\eqref{eq:alternative:MRPI:set} by introducing the set of all possible successor states~$\D_k(X)$ of states in $X$ after $k$ time steps:
%
\begin{align*}
	\D_k(X) &= (A+BK)^{k}X\oplus\W\oplus\dots\oplus(A+BK)^{k-1}\W\\
	&= (A+BK)^k X\oplus \bigoplus_{i=0}^{k-1}(A+BK)^i\W
\end{align*}
%
Defining $\R = (C+DK)^{-1}(\Y\ominus\V^\prime)$ we can abbreviate the conditions defining $X^\infty$ in~\eqref{eq:alternative:MRPI:set} to
%
\begin{equation}\label{eq:containment:condition:alternative:MRPI}
\D_k(X^\infty)\subseteq\X\cap\R
\end{equation}
%
for all $k\geq0$.
%
Using these conditions we can express $X^\infty$ directly as
%
\begin{gather}
X^\infty = %\bigcap_{k\geq0}(A+BK)^{-k}\Bigl((\X\cap\R)\ominus\bigoplus_{i=0}^{k-1}(A+BK)^i\W\Bigr) \\
\bigcap_{k\geq0} \E_k, \\
\E_k = (A+BK)^{-k}\biggl[(\X\cap\R)\ominus\bigoplus_{i=0}^{k-1}(A+BK)^i\W\biggr] . \label{eq:Ek:subtract}
\end{gather}
% \begin{equation}\label{eq:direct:formulation:MRPI:with:intersection}
% 	X^\infty = \bigcap_{k\geq0}\underbrace{(A+BK)^{-k}\left((\X\cap\R)\ominus\bigoplus_{i=0}^{k-1}(A+BK)^i\W\right)}_{\E_k}.
% \end{equation}
%
Due to its definition~$\E_k$ satisfies $\D_k(\E_k)\subseteq\X\cap\R$ for each $k\geq0$, furthermore it can be shown that $\E_k$ expands exponentially and therefore $X^\infty$ is finitely determined  (see Theorem~\ref{thm2} below).
%
In order to compute $X^\infty$ we define the sequence $X_0,X_1,\ldots$ via the iteration:
%
\begin{equation}\label{eq:MRPI:sequence}
\begin{aligned}
  & X_0 = \X\cap K^{-1}\mathcal U \\
  & \begin{aligned}
      & Z_k = X_k\cap\R\\
      & X_{k+1} = Z_k\cap(A+BK)^{-1}(Z_k\ominus\W)
    \end{aligned} 
  \ \Biggr\} \ \ k = 1,2,\ldots
\end{aligned}
\end{equation}
%
%with $X_0= \X$.
Clearly $X_k = \bigcap_{l=0,\ldots,k}\E_l$ and, analogously to the conventional MRPI calculation~\citep{Kolmanovsky:1998}, the iteration therefore gives $X_k = X^\infty$ if $X_k\subseteq X_{k+1}$.

\vspace{0.5\baselineskip}
\begin{thm}\label{thm2}
Let $\Gamma$ be a matrix such that $\Gamma x\leq\bfa{1}$ and $-\Gamma x\leq\bfa{1}$ for all $x\in X_0$ and let $\bigl((A+BK),\Gamma\bigr)$ be observable, then the iteration~\eqref{eq:MRPI:sequence} %terminates after a finite number, $N$, of iterations, such that 
yields $X_{k+1}=X_k$ for all $k\geq N$ and hence $X_k=X^\infty$ for some finite integer $N$.
\end{thm}
%
The matrix~$\Gamma$ is an analytical object and can be made up of~$E_i$ and~$F_iK$, but does not need to contain all inequalities supporting~$X_0$, e.g. in asymmetrical cases.
%
\\[1em]
%
\bpf
%
The observability of the pair $\bigl((A+BK),\Gamma\bigr)$ implies that $X_{d-1}$ is compact, since 
\begin{align*}
X_{d-1} 
&\subseteq\bigcap_{k\leq d-1}(A+BK)^{-k} X_0\\
&\subseteq \Bigl\{x:\pm\Gamma x\leq\bfa{1}\wedge\dots\wedge\pm\Gamma(A+BK)^{d-1} x\leq\bfa{1} \Bigr\}\\
& = \bigl\{x:\pm\Gamma \Obs x\leq \bfa{1}\bigr\}
\end{align*}
where $\Obs$ is the (full rank) observability matrix.

Let~$P$ be such that 
\[
(A+BK)^TP(A+BK) \leq \rho^2P
\]
holds, where $\rho$ denotes the spectral radius of $A+BK$, such a matrix can be found using semi-definite programming.
%
To see that $\E_k$ grows exponentially let $\W\subseteq\B_P(r)$ then
%
\begin{multline*}
  \bigoplus_{i=0}^{k-1}(A+BK)^i\W \subseteq \bigoplus_{i=0}^{k-1}(A+BK)^i\B_P(r)\\
  \subseteq\bigoplus_{i=0}^{k-1}\B_P(\rho^i r) = \B_P\biggl(\sum_{i=0}^{k-1}\rho^i r\biggr)\subseteq\B_P\Bigl(\frac{r}{1-\rho}\Bigr) .
\end{multline*}
%
It follows that the subtrahend in square brackets on the RHS of (\ref{eq:Ek:subtract}) is bounded for all $k$ by $\B_P\bigl(r / (1-\rho)\bigr)$.
%It follows that the RHS of (\ref{eq:Ek:subtract}) consists of an expanding minuend and a bounded subtrahend.
%
Therefore 
%$\E_k$ expands exponentially. Hence 
the iteration (\ref{eq:MRPI:sequence}) must either yield $X_N = \emptyset$ for finite $N$
(in which case $X^\infty=\emptyset$) or,
since $X_{d-1}$ is bounded and $\E_k$ expands exponentially, there must exist a finite $N$ such that $X_{N}\cap\E_{N+1}=X_N$ and hence $X_N=X^\infty$.
%
\epf

@@

In particular, the one-step controllable set $C_1(\T)$ for a polytopic
target set~$\T$
% \[
% \T = \Bigl\{x\in\RR^d : J_i x\leq1,\ i\leq M_\T\Bigr\}
% \]
% is given by the projection of 
%
%In particular, the one-step controllable set $C_1(\T)$ for the polytopic target set~$\T$
% \[
% \T = \Bigl\{x\in\RR^d : J_i x\leq1,\ i\leq M_\T\Bigr\}
% \]
is given by the projection on to the $x$-subspace of the polytopic set $L_1(\T)\subset \RR^{d+q_{\U}}$, 
%$L_1(\T)\subset \RR^d\times \RR^{q_{\U}}$, 
defined by
%
\begin{multline*}
L_1(\T) = \Bigl\{(x,u)\in (\X,\U): \\
\begin{aligned}
& Cx+Du + v\in\Y \\
& Ax+Bu+w\in\T
\end{aligned}\\
\forall v\in\V^\prime,\, \forall w\in\W\Bigr\} .
%\end{aligned}
\end{multline*}
% \begin{equation}
% 	L_1(\T) = \left\{(x,u):\begin{aligned}
% 	x\in\X, u\in\U, Cx+Du + v\in\Y\;\forall v\in\V^\prime,\\
% 	Ax+Bu+w\in\T\;\forall w\in\W
% 	\end{aligned}\right\}
% \end{equation}
%
%onto the $x$-subspace.
%
Thus
\[
C_1(\T) = \{ x\in\mathcal X : \exists u \ \text{such that} \ (x,u)\in L_1(\T)\}.
\]
As all involved sets are polytopic, $L_1(\T)$ is polytopic and its exact projection can be determined computationally.

@@

In order to compare the proposed method with existing results we compute a sample-based set as described in~\cite{Zhang2015}, that is we compute the smallest set $\V^\prime$ containing enough samples to guarantee constraint satisfaction with a confidence of $1-\beta$.
%
To obtain a comparable result we use again constrain $\V^\prime $ to be a scaled version of $\V$, so that $\V^\prime = \{v : \Gamma_i v \leq \gamma_i, \, i =1,\ldots,4\}$, where $\V = \{v : \Gamma_i v \leq 1, \, i =1, \ldots ,4\}$.
%
The optimisation~\citep[eq.~(10)]{Zhang2015} is then given as
%
\begin{subequations}\label{eq:comparison:set}
\begin{equation}\min_{\gamma_1,\dots,\gamma_4} \  \ \sum_{i=1}^4\gamma_i
\end{equation}
subject to 
\begin{equation}
\Gamma_i \hat{v}^{(j)}\leq \gamma_i ,\ i\in\{1,\ldots,4\}, \ j = 1,\ldots,N
\end{equation}
\end{subequations}
% \begin{equation}\label{eq:comparison:set}\begin{split}
% 	\min_{\gamma_1,\dots,\gamma_4}&\quad\sum_{i=1}^4\gamma_i\\
% 	\text{s.t.}&\quad \Gamma_i \bfa{v}^{(j)}\leq \gamma_i ,i\in\{1,\dots,4\}
% \end{split}\end{equation}
%
%$\hat{v}^{(j)}$, $j=1,\ldots,N$

where $\hat{v}^{(1)},\ldots,\hat{v}^{(N)}$ are the samples used to satisfy the probabilistic requirements with the given confidence of $\beta=0.001$. 
%
The number of samples that are needed to satisfy this requirement is given by the cumulative binomial distribution, but can be overestimated to be $N \geq \frac{2}{1-p}(2-\log(\beta))$, so for this example $N = 26$.
%

The resulting sets $\V^\prime$ and $X^\infty$ are shown in Figures~\ref{figure:V:prime:and:comparison} and~\ref{fig:MRPI:optimised}.

%
The set $\V^\prime$ computed using (\ref{eq:comparison:set}a,b) is clearly sub-optimal (Fig.~\ref{figure:V:prime:and:comparison}), and in fact it contains $80.77$\% of the total volume of $\V$.
%
This sub-optimality is a result of the requirement for a high level of confidence ($1-\beta = 0.999$), and is reflected in a reduction in volume of the associated positively invariant set (Fig.~\ref{fig:MRPI:optimised}).

%
\begin{figure}
% \includegraphics[width=.95\linewidth]{Vprime.pdf}
% \caption{The set~$\V^\prime$ resulting the optimisation~\eqref{seq:optimisation:MRPI:precise} for the discussed requirements in \textcolor[rgb]{0.9255,0.6902,0.2078}{yellow} with $\PP\{v\in\V^\prime\}=0.3$, and in \textcolor{red}{red}, the set satisfying~\eqref{eq:comparison:set}, with the defining samples. The comparison set contains $80.77$\% of the total volume of $\V$.}
\includegraphics[width=0.99\linewidth]{Vprime.pdf}
\caption{The set~$\V^\prime$ resulting from the optimisation \mbox{(\ref{seq:optimisation:MRPI:precise}a-d)} with $\PP\{v\in\V^\prime\}=0.3$ in \textcolor[rgb]{0.9255,0.6902,0.2078}{yellow}. 
%
In \textcolor{red}{red}, the set $\V^\prime$ computed using~(\ref{eq:comparison:set}a-b) for a confidence level of $1-\beta=0.999$. 
%
The samples $\{\hat{v}^{(1)},\ldots,\hat{v}^{(26)}\}$ are shown in \textcolor{blue}{blue}.}
\label{figure:V:prime:and:comparison}
% \vspace{2mm}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.99\linewidth]{MRPIsetOptimised.pdf}
\caption{The guaranteed positively invariant set $X^\infty$ computed using~\mbox{(\ref{seq:optimisation:MRPI:precise}a-d)} in \textcolor[rgb]{0,0.5216,0.7373}{blue}, and in \textcolor[rgb]{1,0,0}{dashed red} the robust positively invariant set for the disturbance set $\V^\prime$ computed using~(\ref{eq:comparison:set}a-b) with a confidence level of $1-\beta = 0.999$.}
\label{fig:MRPI:optimised}
\vspace{2mm}\end{figure}

% For the same setup~\eqref{eq:example:system:MRPI} we approximate the guaranteed 3-step controllable set $\C_3(\T)$, where $\T=X^\infty$.
% %
% Again the result illustrated in Figure~\ref{fig:n:step:controllable:set} can be reproduced using different initial values although the Hessian at the maximiser has a non-trivial nullspace.
%
For the same system and constraints (\ref{eq:example:system:MRPI})-(\ref{eq:example:pconstriaint}) we approximate the guaranteed 3-step controllable set $\C_3(\T)$, with $\T=X^\infty$,
%
by solving (\ref{seq:optimisation:n:step:precise}a-d) for $C_1(X^\infty)$, $C_2(X^\infty)$, $C_3(X^\infty)$, where $X^\infty$ is the guaranteed positively invariant set computed via (\ref{seq:optimisation:MRPI:precise}a-d).
%
Again the results illustrated in Figure~\ref{fig:n:step:controllable:set} can be reproduced using different initial values even though the Hessian at the maximiser has a non-trivial nullspace. 
%
The figure also shows the controllable sets that are obtained, for the same target set (i.e.~$\T=X^\infty$), with a fixed set $\V^\prime$ which was computed using the sample based approach of~\citet{Zhang2015} by solving~(\ref{eq:comparison:set}a-b). 
%
Clearly the high level of sub-optimality in this choice of $\V^\prime$, which is a consequence of the requirement for a high level of confidence of satisfaction of the chance constraint, translates to sub-optimality in the computed sets $C_n(X^\infty)$.
\textcolor{red}{Did we not say that 5 sentences ago?}
%
% For the same system and constraints (\ref{eq:example:system:MRPI})-(\ref{eq:example:pconstriaint}) we approximate the guaranteed 3-step controllable set $\C_3(\T)$, where $\T=\{x:\norm{x}_\infty\leq 2\}$
% %
% by solving (\ref{seq:optimisation:n:step:set:abstract}a-c) for $C_1(\T)$, $C_2(\T)$, $C_3(\T)$.
% %
% Again the result illustrated in Figure~\ref{fig:n:step:controllable:set} is reproduced using different initial values although the Hessian at the maximiser has a non-trivial nullspace.
% %

% \begin{figure}
% \includegraphics[width=.95\linewidth]{NStepSetOptimised.pdf}
% \caption{Approximation of the guaranteed 3-step controllable set for a guaranteed positive invariant set $X^\infty$ (\textcolor[rgb]{0.4667,0.6745,0.1882}{in green}). 
% % The additional sets are remaining $C_1(X^\infty),C_2(X^\infty)$ and $C_3(X^\infty)$ dashed for the comparison set obtained with~\eqref{eq:comparison:set} and solid for the optimised~$\V^\prime$ obtained with the proposed method.}
% % \caption{Approximation of the guaranteed 3-step controllable set for a box $\T$ (in blue). 
% Sets $C_1(X^\infty)$, $C_2(X^\infty)$ and $C_3(X^\infty)$ computed by optimising $\V^\prime$ using  (\ref{seq:optimisation:n:step:set:abstract}a-c) are shown in solid lines. For comparison, the controllable sets obtained with~\eqref{eq:comparison:set} with 
% confidence $1-\beta$, $\beta = 0.001$ are shown in dashed lines.}
\begin{figure}[ht]
\includegraphics[width=.99\linewidth]{NStepSetOptimised.pdf}
% \caption{Approximation of the guaranteed 3-step controllable set for a guaranteed positive invariant set $X^\infty$ (in blue). The additional sets are remaining $C_1(X^\infty),C_2(X^\infty)$ and $C_3(X^\infty)$ dashed for the comparison set obtained with~\eqref{eq:comparison:set} and solid for the optimised~$\V^\prime$ obtained with the proposed method.}
\caption{Approximation of the guaranteed 3-step controllable set for a $\T=X^\infty$ (in \textcolor[rgb]{0.4667,0.6745,0.1882}{green}). Sets $C_1(\T)$, $C_2(\T)$ and $C_3(\T)$ computed by optimising $\V^\prime$ using  (\ref{seq:optimisation:n:step:set:abstract}a-c) are shown in solid lines. For comparison, the controllable sets obtained for a fixed $\V^\prime$ computed using~(\ref{eq:comparison:set}a,b) with 
confidence $1-\beta= 0.999$ are shown in dashed lines.}
\label{fig:n:step:controllable:set}
\vspace{4mm}\end{figure}
